Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-16 paper/paper.tex
Muck around with float placement
More graphery. Will improve these later.

\begin{figure}[t]
    \centering
    \input{graph-cumulative}\vspace{-0.5cm}

@@

@@

\begin{table}[t]
\begin{center}
\begin{tabularx}{.8\textwidth}{XXrXrrrXrrrr}
\toprule
Class && \VFtwo && \multicolumn{3}{c}{\LAD} && \multicolumn{4}{c}{\hspace*{2em}\Glasgow}\\
&&&&incomplete&default&path&&1&2&3&4\\
\midrule
1 &&        0 &&       20 &        0 &        0 &&       80 &        0 &        0 &        0 \\
2 &&      201 &&       92 &      189 &      270 &&      520 &      180 &       53 &       15 \\
3 &&      112 &&     1608 &      617 &      959 &&      396 &      195 &       21 &        0 \\
4 &&      270 &&        0 &        0 &        0 &&        5 &        0 &        0 &        0 \\
5 &&      266 &&        0 &        1 &        3 &&       31 &        0 &        0 &        0 \\
6 &&       71 &&        0 &        0 &        0 &&        7 &       14 &        1 &        0 \\
7 &&      270 &&        0 &        0 &        0 &&        5 &        0 &        0 &        0 \\
8 &&        0 &&        0 &        0 &        1 &&      195 &       69 &        6 &        0 \\
9 &&       77 &&        3 &        0 &       19 &&      103 &        1 &        0 &        0 \\
10 &&       13 &&        0 &        2 &        2 &&        7 &        0 &        0 &        0 \\
11 &&        2 &&      142 &       71 &       17 &&       23 &        0 &        0 &        0 \\
12 &&        0 &&        0 &        1 &        2 &&      158 &        6 &        1 &        0 \\
\midrule
Total && 1282 && 1865 & 881 & 1273 && 1530 & 465 & 82& 15\\
\bottomrule
\end{tabularx}
\end{center}
\caption{Number of times each algorithm is best, for each class.\label{expClass}}
\end{table}

@@

\begin{table}[ht]
    \centering\setlength{\tabcolsep}{1em}
\begin{tabular}{lrrr}
  \toprule
model & mean MCP & solved instances & mean performance\\
  \midrule
virtual best & 0 & 2219 & 5822809\\
\LLAMA & 610835 & 2206 & 6435301\\
\GlasgowTwo & 1965158 & 2172 & 7787967\\
   \bottomrule \\
\end{tabular}
\caption{Algorithm selection performance on the reduced set of 2336
instances. MCP is the misclassification penalty; that is, the additional time
required to solve an instance because of choosing solvers that perform
worse than the best.}\label{tab:res}
\end{table}

@@

\begin{table}[ht]
    \centering\setlength{\tabcolsep}{1em}
\begin{tabular}{lrrr}
  \toprule
model & mean MCP & solved instances & mean performance\\
  \midrule
virtual best & 0 & 5608 & 2375913\\
\LLAMA & 249242 & 5595 & 2625831\\
\GlasgowTwo & 798660 & 5562 & 3174573\\
   \bottomrule \\
\end{tabular}
\caption{Algorithm selection system performance on the full set of 5725
instances.}\label{tab:resfull}
\end{table}

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figures/portfolio-ecdf}
\caption{Number of solved instances over time for solvers, virtual best
solvers, and \LLAMA on the reduced set of 2336 instances. The
actual solvers are shown as dashed lines.}
\label{fig:portfolio-ecdf}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figures/portfolio-ecdf-full}
\caption{Number of solved instances over time for solvers, virtual best
solvers, and \LLAMA on the full set of 5725 instances. The
actual solvers are shown as dashed lines.}
\label{fig:portfolio-ecdf-full}
\end{figure}

>>>>

\begin{figure}[p]
    \centering
    \input{graph-cumulative}\vspace{-0.5cm}

@@

\begin{table}[p]
\centering
\begin{tabularx}{.8\textwidth}{XXrXrrrXrrrr}
\toprule
Class && \VFtwo && \multicolumn{3}{c}{\LAD} && \multicolumn{4}{c}{\hspace*{2em}\Glasgow}\\
&&&&incomplete&default&path&&1&2&3&4\\
\midrule
1 &&        0 &&       20 &        0 &        0 &&       80 &        0 &        0 &        0 \\
2 &&      201 &&       92 &      189 &      270 &&      520 &      180 &       53 &       15 \\
3 &&      112 &&     1608 &      617 &      959 &&      396 &      195 &       21 &        0 \\
4 &&      270 &&        0 &        0 &        0 &&        5 &        0 &        0 &        0 \\
5 &&      266 &&        0 &        1 &        3 &&       31 &        0 &        0 &        0 \\
6 &&       71 &&        0 &        0 &        0 &&        7 &       14 &        1 &        0 \\
7 &&      270 &&        0 &        0 &        0 &&        5 &        0 &        0 &        0 \\
8 &&        0 &&        0 &        0 &        1 &&      195 &       69 &        6 &        0 \\
9 &&       77 &&        3 &        0 &       19 &&      103 &        1 &        0 &        0 \\
10 &&       13 &&        0 &        2 &        2 &&        7 &        0 &        0 &        0 \\
11 &&        2 &&      142 &       71 &       17 &&       23 &        0 &        0 &        0 \\
12 &&        0 &&        0 &        1 &        2 &&      158 &        6 &        1 &        0 \\
\midrule
Total && 1282 && 1865 & 881 & 1273 && 1530 & 465 & 82& 15\\
\bottomrule \\
\end{tabularx}
\caption{Number of times each algorithm is best, for each class.\label{expClass}}
\end{table}

@@

@@

\begin{table}[p]
    \centering\setlength{\tabcolsep}{1em}
\begin{tabular}{lrrr}
  \toprule
model & mean MCP & solved instances & mean performance\\
  \midrule
virtual best & 0 & 2219 & 5822809\\
\LLAMA & 610835 & 2206 & 6435301\\
\GlasgowTwo & 1965158 & 2172 & 7787967\\
   \bottomrule \\
\end{tabular}
\caption{Algorithm selection performance on the reduced set of 2336
instances. MCP is the misclassification penalty; that is, the additional time
required to solve an instance because of choosing solvers that perform
worse than the best.}\label{tab:res}
\end{table}

\begin{figure}[p]
\input{graph-reduced}

\caption{Number of solved instances over time for the virtual best
solver, \LLAMA, and individual solvers (shown as dotted lines, in the same
colours as Figure~\ref{expTimeGraph}) on the reduced set of 2336 instances.}
\label{fig:portfolio-ecdf}
\end{figure}

@@

@@

\begin{table}[p]
    \centering\setlength{\tabcolsep}{1em}
\begin{tabular}{lrrr}
  \toprule
model & mean MCP & solved instances & mean performance\\
  \midrule
virtual best & 0 & 5608 & 2375913\\
\LLAMA & 249242 & 5595 & 2625831\\
\GlasgowTwo & 798660 & 5562 & 3174573\\
   \bottomrule \\
\end{tabular}
\caption{Algorithm selection system performance on the full set of 5725
instances.}\label{tab:resfull}
\end{table}

\begin{figure}[p]
    \input{graph-full}
\caption{Number of solved instances over time for solvers, virtual best
solvers, and \LLAMA on the full set of 5725 instances. The
actual solvers are shown as dashed lines.}
\label{fig:portfolio-ecdf-full}
\end{figure}
